Circumcision Paper Text

### 2024-04-11 paper/paper_cals.Rmd
Finish section 2

@@

The disparity between the number of MCs performed and the number of MMCs performed can be explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or TMC.

@@

) in 2020, staying relatively stagnant. 

@@

@@

@@

The mean age at circumcision for MC in 2006 was 
x
(
x
- 
x
), while in 2020 it was
x 
(
x
-
x
).
Similarly, the mean age at circumcision for MMC in 2006 was 
x
(
x
- 
x
), while in 2020 it was
x 
(
x
-
x
).
Finally, the mean age at circumcision in 2006 for TMC was 
x
(
x
- 
x
), while in 2020 it was
x 
(
x
-
x
).
So the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
However, it is important to note that the uncertainty ranges in our credible intervals 
overlap, so this increase is ?. 
In constant, the mean age at circumcision for TMC decreased. 
This may suggest that VMMC implementation amongst 15-29 year olds has 
corresponded to an upward shift of mean age at circumcision for MC and MMC, and 
replaced some circumcisions which would previously have been performed as TMCs, 
which may explain the observed decrease in mean age of TMC.

>>>>

<!-- What else could we add to this section? Section 2 is very large!!!
- Could talk about non-VMMC vs VMMC more anyway -->

@@

The disparity between the number of MCs performed and the number of MMCs performed can be partly explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or TMC.

@@

) in 2020, staying relatively similar. 

@@

TMC coverage decreased more amongst non-VMMC countries for both age groups, suggesting 
likely replacement of historical TMC with MMC.

@@

```{r}

```

@@

The mean age at circumcision for MC in 2006 was 
x

(
x
- 
x
), while in 2020 it was
x 
(
x
-
x
).
Similarly, the mean age at circumcision for MMC in 2006 was 
x
(
x
- 
x
), while in 2020 it was
x 
(
x
-
x
).
Finally, the mean age at circumcision in 2006 for TMC was 
x
(
x
- 
x
), while in 2020 it was
x 
(
x
-
x
).
So the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
However, it is important to note that the uncertainty ranges in our credible intervals 
overlap, so this increase is ?. 
In constant, the mean age at circumcision for TMC decreased. 
This may suggest that VMMC implementation amongst 15-29 year olds has 
corresponded to an upward shift of mean age at circumcision for MC and MMC, and 
replaced some circumcisions which would previously have been performed as TMCs, 
which may explain the observed decrease in mean age of TMC.
